A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2018-11-28 MS.tex
Added author summary as per PLOS guidelines

\section{Author summary}

>>>>

\section{Author summary}
Mosquitoes transmit some of the most important diseases afflicting humans, with malaria alone killing between 0.4-1.2 million people annually, chiefly children in low-income countries. The transmission strength of these diseases depends critically on the duration of mosquito lifespans and some of the most successful disease control interventions, including insecticide-treated bednets, explicitly target reductions in mosquito longevity. In this study, we conduct meta-analyses of two important classes of field experiments which estimate wild mosquito lifespan: mark-release-recapture studies, where mosquitoes are marked with a dye then released with the number of marked mosquitoes caught monitored over time; and experiments involving dissection of wild-caught females, whose reproductive anatomy is used as a biological clock to determine physiological age. In both analyses, we estimate that most mosquito species live less than 10 days, on average, which suggests that relatively few mosquitoes live sufficiently long to transmit disease. We find evidence of variation in mosquito mortality across species, with the estimates of lifespan obtained from each method largely corresponding for the few species with data from both experiments. Finally, by fitting a range of survival models to the data, we conclude that, for most species, mosquitoes do not experience strong age-related increases in mortality.
